Log\+Viewer is a python script which is able to parse an ftp log extracting the useful information and uploading them to a common Influx\+DB database.

A vsftpd server will, by default, store its log in /var/log/vsftpd.log. This path can be edit in the vsftpd.\+conf file, in the same file can also be decided the log form. A log in F\+TP can be saved in a standard form or in xferlog standard form, there is not much difference in the reported data, the real difference is in the form in which they are shown.

To explain how the script works is better to analyze it throw a few steps.

{\bfseries{S\+T\+EP O\+NE\+:}}

First thing the script does is search inside a specific directory all the log file that are stored. This is done because may be more than one server running at the same time on the same hardware so having a shared directory for the log can help reduce waste. Each file is then opened, and a dedicated thread object is created and started.

{\bfseries{S\+T\+EP T\+WO\+:}}

First thing the script does is search inside a specific directory all the log file that are stored. This is done because may be more than one server running at the same time on the same hardware so having a shared directory for the log can help reduce waste. Each file is then opened, and a dedicated thread object is created and started.

{\bfseries{S\+T\+EP T\+H\+R\+EE\+:}}

The pointer to the file is now moved at the end of the file and the thread enter in a while True loop where constantly check if new line have been added to the file. If there isn’t any new entry the thread suspend itself for a couple of seconds.

{\bfseries{S\+T\+EP F\+O\+UR\+:}}

When a new line is found inside the log there is a first check to ensure it is a confirmed download operation and not an upload or login operation. If the line respects this property, the script proceeds to parse the request with the purpose to isolate some crucial information. To do that an object Request is created. This process will end with the creation of a J\+S\+ON object.

{\bfseries{S\+T\+EP F\+I\+VE\+:}}

Now that the request has been parsed the new entry is entered in the influx\+DB database throw a simple I\+N\+S\+E\+RT query. The connection and writing method are managed by an opposite class. 